Simulating Single Cell experiments from ScPCA data

### 2024-03-14 analyses/simulate-sce/notebooks/splatter-ScPCA.Rmd
Spelling updates
Flesh out readme and update notebook intro a

@@

Modify the cluster and cell type labels in the subest SCE to ensure they are all represented

>>>>

This notebook was used as exploration for the `simulate-sce.R` script.
The code here is not fully current with that script, but has been left here for reference about the development process and for future use.

@@

Modify the cluster and cell type labels in the subset SCE to ensure they are all represented
